What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-09 lda-paper.tex
pLSI

Topic analysis, with respect to Software Control Systems (SCSs) such
as CVS, Subversion, Git etc., is potentially valuable as it has many
uses for various stake-holders and uses.  Imagine a development team
has agreed to implement some features at the start of an iteration. By
the end of the iteration only some of the agreed upon features are
implemented. The developers insist they were focusing solely on the
features agreed upon, but what actually happened? Topic analysis could
help by teasing out the distinct topics or focusses of the
developers. Perhaps the developers had to deal with issues.
Developers might have grouped those orthogonal changes into one of the
features they were working on, thus when asked about how their time
was spent the orthogonal changes would not be covered. This is the kind of underlying story that we
hope that windowed topic analysis can uncover. If windowed topic
analysis can discover important but overlooked topics, it can help
both developers and managers. Developer can see a summary of what
worked on, and managers can development.

@@

%XXX explain LDA \cite{944937}
%XXX What has pLSI in it?
In terms of clustering and finding topic distributions, Latent
Dirichlet Allocation (LDA)~\cite{944937} competes with Latent Semantic
Indexing (LSI)~\cite{1421013,1374321,10.1109/ICPC.2007.13,10.1109/ICPC.2006.17}, probabilistic Latent Semantic Indexing (pLSI) and
semantic clustering~\cite{1698774,1566153}. These tools are used for document modelling,
document clustering and collaborative filtering. What LDA attempts to
do is encode documents as mixture model of topics.  LDA is used in
software engineering
literature~\cite{lukins2008,10.1109/MSR.2007.20,NIPS2007637,1321709}
is to extract topic clusters from documents such as methods, bug
reports, source code and files.

@@

%XXX Describe something useful like a trend
\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \caption{Compact Trend Plot Topics per Month for MaxDB 7.500. The
    X-axis is time in months, the Y axis is used to stack topics
    occurring at the same time. Trends that are continuous are
    plotted as continuous blocks. The top 10 words in the topics are
    joined and embedded in box representing the topics.}
  \label{fig:topicsmear}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend-time Line: Trends plotted over time of MaxDB 7.500. Time in months are plotted along the X-Axis, each row on the Y-axis is associated with a trend ranked by size in descending order}         
  \label{fig:trendtimeline}
\end{figure}

@@

Our analysis tools consisted of: Hiraldo-Grok, an OCaml-based variant
of the Grok query language; Gnuplot, a graph plotting package; lda-c,
a LDA package implemented by Biel; and our topic plotter, implemented
in Haskell.

@@

% The thing that is most disappointing is that the argument is entire qualitative.  Can you give examples to make this sound less hypothetical?

>>>>

Topic analysis, with respect to Software Control Systems (SCSs) such
as CVS, Subversion, Git etc., is potentially valuable as it has many
uses for various stakeholders and uses.  Imagine a development team
has agreed to implement some features at the start of an iteration. By
the end of the iteration only some of the agreed upon features are
implemented. The developers insist they were focusing solely on the
features agreed upon, but what actually happened? Topic analysis could
help by teasing out the distinct topics or focusses of the
developers. Perhaps the developers had to deal with issues.
Developers might have grouped those orthogonal changes into one of the
features they were working on, thus when asked about how their time
was spent the orthogonal changes would not be covered. This is the kind of underlying story that we
hope that windowed topic analysis can uncover. If windowed topic
analysis can discover important but overlooked topics, it can help
both developers and managers. Developer can see a summary of what
worked on, and managers can development.

@@

In terms of clustering and finding topic distributions, Latent
Dirichlet Allocation (LDA)~\cite{944937} competes with Latent Semantic
Indexing
(LSI)~\cite{1421013,1374321,10.1109/ICPC.2007.13,10.1109/ICPC.2006.17},
probabilistic Latent Semantic Indexing (pLSI)~\cite{944937} and
semantic clustering~\cite{1698774,1566153}. These tools are used for
document modelling, document clustering and collaborative
filtering. What LDA attempts to do is encode documents as mixture
model of topics.  LDA is used in software engineering
literature~\cite{lukins2008,10.1109/MSR.2007.20,NIPS2007637,1321709}
is to extract topic clusters from documents such as methods, bug
reports, source code and files.

@@

%XXX Describe something useful like a trend
\begin{figure*}
  \centering
  \includegraphics[width=1.0\textwidth]{fixed-time-smear-plot-scaled}
  \caption{Compact Trend Plot Topics per Month for MaxDB 7.500. The
    x-axis is time in months, the Y axis is used to stack topics
    occurring at the same time. Trends that are continuous are
    plotted as continuous blocks. The top 10 words in the topics are
    joined and embedded in box representing the topics.}
  \label{fig:topicsmear}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{class-smear-plot-crop-scaled}
  \caption{Trend-time Line: Trends plotted over time of MaxDB 7.500. Time in months are plotted along the x-Axis, each row on the y-axis is associated with a trend ranked by size in descending order}         
  \label{fig:trendtimeline}
\end{figure}

@@

Our analysis tools consisted of: Hiraldo-Grok, an OCaml-based variant
of the Grok query language; Gnuplot, a graph plotting package; lda-c,
a LDA package implemented by Blei et al. \cite{944937}; and our topic plotter, implemented
in Haskell.

@@

% The thing that is most disappointing is that the argument is entire
% qualitative.  Can you give examples to make this sound less
% hypothetical?
